### 2025-04-29 paper/paper.tex

\newpage 
Concretely, the helper function
\begin{verbatim}
build_mlp(input_dim, output_dim, 
hidden_layers):
    layers   = []
    prev     = input_dim
    for h in hidden_layers:
        layers.append(nn.Linear(prev, h))
        layers.append(nn.ReLU())
        prev = h
    layers.append(nn.Linear(prev, 
    output_dim))
    return nn.Sequential(*layers)
\end{verbatim}
constructs the sequential network, allowing us to easily swap hidden layer sizes or depths via configuration.

@@

Testing the average trip time was one of the most important benchmarks implemented, since longer trips result in less cars on the road and a shorter time spent on the road, the odds of a traffic incident decreases dramatically. When using traditional threshold signals the average trip time took 695.34 seconds, or 11 minutes and 34 seconds. When using neural network based traffic signals a noteable decrease in average trip time was observed, decreasing to 587.61 seconds, or 9 minutes and 47 seconds. With a nearly 108 second decrease in average trip time, we saw a 15\% reduction in average trip time.

@@

Another important metric to decrease it the average length of stopped cars at any point in time, known as the average queue length. Because our wait time decreased, we can expect a noteable decrease in average queue length, as less cars need to stop and wait. This is confirmed, as we achieve an average queue length of 230 vehicles with threshold neural networks, and a queue length of 55 vehicles when using neural networks. This is an astronomical decrease, with an average of 175 less vehicles being stopped at any point in time.  This is a nearly 76\% decrease in average queue length, indicating a significant imporvement in performance over baselines.

Fianlly, the maximum length of cars was determined in order to ensure that traffic did not ever back up very bad. Because the average queue length decreased greatly, it is safe to assume that the maximum queue length decreased significantly, which is confirmed by our results. When using traditional threshold signals the maximum queue length reached 1373 vehicles, and the maximum queue length reached 316 vehicles. This indicates that the peak congestion was significantly improved through our model over baselines, preventing large backups which can be frustrating and potentially dangerous.

>>>>

Concretely, the helper function
\begin{verbatim}
build_mlp(input_dim, output_dim, 
hidden_layers):
    layers   = []
    prev     = input_dim
    for h in hidden_layers:
        layers.append(nn.Linear(prev, h))
        layers.append(nn.ReLU())
        prev = h
    layers.append(nn.Linear(prev, 
    output_dim))
    return nn.Sequential(*layers)
\end{verbatim}
constructs the sequential network, allowing us to easily swap hidden layer sizes or depths via configuration.

@@

Testing the average trip time was one of the most important benchmarks implemented, since longer trips result in less cars on the road and a shorter time spent on the road, the odds of a traffic incident decreases dramatically. When using traditional threshold signals the average trip time took 695.34 seconds, or 11 minutes and 34 seconds. When using neural network based traffic signals a notable decrease in average trip time was observed, decreasing to 587.61 seconds, or 9 minutes and 47 seconds. With a nearly 108 second decrease in average trip time, we saw a 15\% reduction in average trip time.

@@

Another important metric to decrease it the average length of stopped cars at any point in time, known as the average queue length. Because our wait time decreased, we can expect a notable decrease in average queue length, as less cars need to stop and wait. This is confirmed, as we achieve an average queue length of 230 vehicles with threshold neural networks, and a queue length of 55 vehicles when using neural networks. This is an astronomical decrease, with an average of 175 less vehicles being stopped at any point in time.  This is a nearly 76\% decrease in average queue length, indicating a significant improvement in performance over baselines.

Finally, the maximum length of cars was determined in order to ensure that traffic did not ever back up very bad. Because the average queue length decreased greatly, it is safe to assume that the maximum queue length decreased significantly, which is confirmed by our results. When using traditional threshold signals the maximum queue length reached 1373 vehicles, and the maximum queue length reached 316 vehicles. This indicates that the peak congestion was significantly improved through our model over baselines, preventing large backups which can be frustrating and potentially dangerous.
